---
title: "Week3"
subtitle: "Group7"
author: 
  - Wendy Yuan
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "This is the activity reflection from the third week in sta304. We learned about static communication & writing reports this week."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @Rcode, @opendatatorotno, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection

# Data {#sec-mydatasection}

Some of our data is of marriage (@fig-marriage), from @opendatatoronto.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```


@opendatatoronto provided data about marriages. Using this data, I generated a graph @fig-marriage. It can be seen that the x axis is the date and the y axis is the number of marriage licenses handed out per month. The graph displays that the marriage licenses given out are more sporadic while prior to covid there was a sin pattern.  


\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


